Concurrent Programming in Harmony

### 2022-01-06 book/paper.tex
Latest

>>>>

It is even cooler to remove that assertion and let Harmony generate
all possible solutions to the problem like so:

\begin{code}
\begin{verbatim}
$ harmony -o hanoi.png code/hanoi.hny
\end{verbatim}
\end{code}

The resulting \texttt{hanoi.png} file contains a DFA describing
the possible solutions.  It is a little too big to include here,
but well worth looking at.
